\documentclass[a4paper,11pt]{article}

% Packages
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
% Add natbib for author-year or numeric citations
\usepackage{hyperref}
\usepackage{url}
\usepackage[margin=2.5cm]{geometry}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{longtable}
\usepackage{rotating}
\usepackage{comment}
\usepackage{csvsimple}
\usepackage{subcaption}
\usepackage[htt]{hyphenat}
\usepackage{xcolor}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}

\usepackage{lipsum}
\usepackage{xcolor}
\definecolor{epflred}{HTML}{FF0000}
\usepackage{listings}
\usepackage{booktabs}
\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny
}
\urlstyle{tt}
\usepackage[backend=biber,style=nature]{biblatex}
\addbibresource{bibliography.bib}
\newcommand{\feat}[1]{\texttt{\nolinkurl{#1}}}




\begin{document}


% Custom EPFL front page
\input{frontpage}

\newpage

\null
\thispagestyle{empty}

\newpage

\pagenumbering{roman}

\input{sections/acknowledgements}

\newpage

\null
\thispagestyle{empty}

\newpage

\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

Continuous high-bandwidth wireless data transmission from a miniaturised fully
implantable neural interface imposes a sustained power demand that a
thin-film-compatible battery cannot maintain over experimentally relevant timescales.
Wireless power transfer~(WPT) is therefore required to enable long-term,
uninterrupted operation without transcutaneous connections. This work presents a
wireless neural recording and stimulation system targeting surface neural recordings such as electrocorticography and spinal cord
recordings (e.g., rat spinal cord).
The system comprises a peripheral nRF52832 module interfacing with an Intan RHS2116
16-channel neural recording and stimulation chip via SPI, a central nRF52832 device
receiving data over Bluetooth Low Energy~(BLE), and a Python-based graphical user
interface for real-time visualisation, configuration, and stimulation control.

The central design contribution is the replacement of the CPU-polling acquisition loop
used in a prior single-channel implementation with a fully hardware-driven pipeline based
on the nRF52832's Programmable Peripheral Interconnect~(PPI) subsystem and EasyDMA.
This decouples data acquisition almost entirely from CPU availability, eliminating
sample jitter caused by SoftDevice radio preemption and enabling the processor to remain
in low-power sleep between BLE connection events. The system supports a configurable
selection of 1--16 recording channels at adjustable per-channel sampling rates up to
32\,kHz, charge-balanced biphasic electrical stimulation with per-channel amplitude and
timing control, and persistent configuration storage in non-volatile flash memory.

BLE throughput with real SPI data reached up to approximately 540\,kbps in the
16-channel, 2\,kHz-per-channel configuration, confirming that the hardware-driven
pipeline sustains the required data rate. Faithful reconstruction of a 300\,Hz, 1\,mV sinusoidal test signal was confirmed
across a range of channel-count and sampling-rate configurations; representative
results for the 16-channel, 2\,kHz-per-channel and 8-channel, 4\,kHz-per-channel
configurations are presented.
The nRF52832 peripheral module consumed 18.6\,mW (equivalent to 20.4\,mW at 3.3\,V),
a 31\,\% reduction compared to the prior single-channel implementation, while
simultaneously increasing the channel count 16-fold. Combined system power
(nRF52832\,+\,Intan RHS2116) was 61.3\,mW at 3.6\,V (48.6\,mW at 3.0\,V),
where 3.6\,V is the nominal WPT output voltage chosen to account for expected
voltage drops in thin-film integration. Most significantly, end-to-end operation of the complete recording and BLE data
transmission pipeline under wireless power was demonstrated with a compact WLCSP49
nRF52832 module ($2.956\times3.226$\,mm), validating the full wireless architecture ---
no wired power supply required. Electromagnetic interference measurements identified
external carrier board wiring as the dominant noise pickup mechanism, with
interference reduced approximately 200-fold by shorting
a channel directly on the Intan die, pointing to PCB co-integration as the
decisive next step toward WPT compatibility.

\newpage

\null
\thispagestyle{empty}


\newpage

% \input{sections/acronyms.tex}

%\newpage

\null
\pagestyle{empty}
\setcounter{tocdepth}{2}
\tableofcontents

\newpage

\null

\newpage


\pagestyle{plain}
\pagenumbering{arabic}

\input{sections/introduction}

\newpage

\input{sections/methods}

\newpage

\input{sections/results}

\newpage

\input{sections/discussion}

\newpage

\input{sections/conclusion}

\newpage

\addcontentsline{toc}{section}{References}
\pagestyle{plain}
\printbibliography
\newpage
\pagestyle{plain}

\input{sections/supplementary_material}


\end{document}
