\section{Conclusion}

This work demonstrates a complete wireless neural recording and stimulation system
built on off-the-shelf components and validated across all major functional blocks.
The central contribution is the replacement of a CPU-polling acquisition loop with a
fully hardware-driven pipeline using the nRF52832 PPI subsystem and EasyDMA, which
decouples data acquisition from CPU availability and eliminates the sample jitter
inherent in software-scheduled SPI transactions. The result is a system that sustains
BLE throughput of up to approximately 540\,kbps with real neural acquisition data
across a configurable selection of 1--16 channels --- a capability the prior
implementation could not demonstrate even with synthetic data.

The hardware-driven architecture yields a measurable power benefit: the nRF52832
peripheral module consumes 20.4\,mW at a nominal 3.3\,V supply, a 31\,\% reduction
compared to the 29.4\,mW reported by the prior single-channel CPU-polling
implementation, achieved while increasing the channel count 16-fold. Two architectural
changes account for this: the PPI/DMA pipeline allows the CPU to remain in low-power
sleep between BLE connection events, and removal of the UART peripheral eliminates a
further source of continuous power draw. Combined system power (nRF52832 and Intan
RHS2116) was measured at 61.3\,mW at 3.6\,V across all tested configurations, with
power scaling approximately as $V^{1.47}$ between 3.0\,V and 3.6\,V supply.

The most significant system-level result is the first end-to-end demonstration of
the complete recording and BLE data transmission pipeline powered entirely by
wireless power transfer, using the compact WLCSP49 nRF52832 module
($3.0 \times 3.2$\,mm) with no wired power supply. Electromagnetic interference measurements
inside the WPT transmitter coil field revealed that carrier board wiring --- rather
than the WPT field acting directly on the silicon --- is the dominant noise pickup
mechanism: shorting a channel directly on the Intan die reduced interference
approximately 200-fold (two orders of magnitude) compared to the carrier board
configuration. This finding clarifies the path forward: PCB co-integration of the
nRF52832 and Intan RHS2116 on a single substrate with short, shielded traces is the
key step toward WPT compatibility, rather than a fundamental redesign of the wireless
architecture.

This co-integration has already been prototyped in the flex PCB described in this
work; the immediate next step is to correct the hardware fault in the current revision
(non-functional on-board oscillator) and characterise the flex PCB inside the WPT
field. Beyond this, the design should be realised as a microfabricated device on a
thin-film substrate, combining the recording and stimulation electronics, the electrode
interface, and the WPT receiver components (RX coil, rectifier, and voltage regulation)
in a single compact, biocompatible assembly. Validation should then proceed first in
vitro, confirming signal integrity and noise performance in a controlled environment,
before advancing to chronic in vivo implantation in the rat spinal cord model for which
this system was designed.
