\clearpage
\section{Discussion}
\label{sec:discussion}

\subsection{Electromagnetic Interference in the WPT Field}

At 30\,cm from the transmitter coil, the recorded noise on a GND-shorted channel
is typically within $\pm10$\,\textmu{}V (20\,\textmu{}V$_\text{pp}$), only
marginally above the amplifier's intrinsic noise floor of
$\approx15.8$\,\textmu{}V$_\text{pp}$. However,
interference grows rapidly with proximity, and inside the coil the amplifier input
saturates entirely. The direct on-chip measurement --- shorting a channel with no
carrier board wiring --- reduced the interference to $\pm20$--$30$\,\textmu{}V
even inside the coil --- an approximately 200-fold reduction relative to the
$-6000$ to $+4000$\,\textmu{}V saturation observed with the carrier board. This confirms that the
carrier board wiring, rather than the WPT field acting directly on the silicon, is
the dominant pickup path: long external wires form inductive loops and act as
antennas in the alternating magnetic field.

The implication is that the interference problem is primarily a packaging problem,
not an intrinsic incompatibility between BLE-based neural recording and WPT.
A co-integrated PCB with short, shielded traces connecting the nRF52832 and Intan
RHS2116 would probably substantially reduce pickup loop area and antenna length. The
prototype flex PCB (Figure~\ref{fig:miniaturization}d) represents exactly this
direction; its oscillator circuit was non-functional in the current revision, but
the hardware fault is unrelated to the interference mechanism and does not
undermine this conclusion.

\subsection{Ring Buffer Architecture}
\label{sec:discussion_ringbuffer}

The periodic power spikes visible in the timecourse data arise from CPU activity
at each DMA buffer swap: copying samples from the inactive DMA buffer into the
ring buffer and assembling BLE packets. An alternative architecture could transmit
data directly from the inactive DMA buffer, potentially reducing these spikes.

The ring buffer's role is twofold. First, it stores only the selected channels at
2\,bytes per sample, whereas the DMA buffers store all 16 channels at 4\,bytes
each; in a 2-channel recording each ring buffer slot is 16$\times$ more compact
per acquisition cycle than a DMA slot. This efficiency is per-sample only: the
current architecture still allocates two full DMA buffers alongside the ring
buffer (three buffers in total), so the overall memory footprint is not reduced
16$\times$. The practical benefit of the ring buffer's compactness is that it
can hold many more samples in the available RAM, giving the BLE stack headroom
to fall behind temporarily without overwriting unread data. Second, the ring
buffer cleanly separates the SPI write path from the BLE read path: the DMA
pipeline writes to the inactive buffer only and the CPU reads from it only once
per swap, so no locking is needed.

Bypassing the ring buffer has two realisations with different trade-offs.
\emph{Option A} (two buffers total): retain the current design's two-buffer
\emph{ping-pong} scheme --- two separate EasyDMA buffers, where hardware writes
to one while the CPU reads from the other, then the roles swap --- but transmit
directly from the inactive buffer instead of copying it into a ring buffer first.
Because the same ping-pong scheme is kept, each buffer swap is still a single
clean handover --- the old buffer is entirely finished and safe to read the
moment the swap happens, exactly as in the current design. However, if
\texttt{CONVERT(63)} is retained, the DMA buffers store all
16 channels at 4\,bytes each --- no channel filtering --- so each buffer holds far
fewer effective samples of the selected channels, and the system can tolerate
fewer BLE delays before data is overwritten. Switching to a
\texttt{CONVERT($k$)}-based acquisition for only the selected channels would avoid
storing unneeded channels, improving on this; each sample would still occupy
4\,bytes (the fixed EasyDMA word size) rather than the ring buffer's 2\,bytes,
so this would only partially close the gap to the current architecture.
\emph{Option B} (one buffer total): replace the two ping-pong EasyDMA buffers with
a single, larger EasyDMA buffer that the firmware operates \emph{as if} it were a
ring buffer, transmitting directly from it instead of using a separate
CPU-managed ring buffer as in the current design. Because the full buffer
capacity is available as a continuous queue rather than being split between a
write half and a read half, this gives twice the BLE delay tolerance of Option~A
for the same total memory. In the ping-pong
scheme, each buffer swap is a single clean handover: the moment it happens, the
old buffer is entirely finished and safe to read, with no risk of the writer
touching it again. A single EasyDMA buffer pressed into service as a circular
buffer has no such clean handover point --- the SPI write pointer and BLE read
pointer continuously move through the same memory, so the firmware must
continually check that the read pointer never falls so far behind that the write
pointer catches up and overwrites data not yet sent.

A single circular buffer also reintroduces the wraparound problem already solved
for the stimulation TX buffer (Section~\ref{sec:stim_architecture}): EasyDMA lists
do not wrap automatically once exhausted, so the CPU must manually reset the write
pointer back to the start each time the list end is reached, and this reset could
itself be delayed if the CPU is busy elsewhere (e.g.\ servicing a SoftDevice ISR).
The same mitigation already used for the existing buffer swap could apply here:
triggering the wraparound early, at some threshold below full capacity (e.g.\
80\,\%, as in the current 819-of-1024 threshold), and reading the actual EasyDMA
write pointer at the moment of the reset rather than assuming the threshold was
reached exactly --- leaving headroom to absorb any delay in the CPU servicing the
reset.

Even so, Option~B is probably still worse than the current
architecture for low channel counts: at 2\,channels the ring buffer stores data
at 2\,channels\,$\times$\,2\,bytes per cycle, whereas an unfiltered DMA buffer
(using \texttt{CONVERT(63)}) stores 16\,channels\,$\times$\,4\,bytes --- a
16$\times$ difference that outweighs the 2$\times$ gain from removing ping-pong.
As with Option~A, using \texttt{CONVERT($k$)} instead would store only the
selected channels, narrowing this gap considerably, though the fixed 4-byte
EasyDMA word size means it would still be only half as compact per sample as the
ring buffer.

This optimisation is left for future work if power becomes the primary
constraint.

\subsection{Limitations}

All measurements in this work were performed with the Intan RHS2116 mounted on its
carrier board, connected via long inter-board wiring and a 40-pin connector board.
This assembly is not representative of a final implantable form factor, and its
wiring is the dominant source of WPT-induced interference (Section~\ref{sec:results_noise}).
The direct on-chip measurement establishes a lower bound on what a co-integrated
solution would achieve, confirming with a shorted (zero-signal) channel that
removing the carrier board and long cables substantially reduces interference.
However, the corresponding claim for a real signal --- that an actual neural-like
input remains recoverable without the carrier board, inside the WPT field ---
could not be directly verified: the prototype flex PCB that was intended to
provide such a signal via its on-board oscillator had a non-functional oscillator
circuit and could not be characterised inside the WPT field.

Power measurements were likewise performed with this bench assembly. The power
figures reported here therefore include contributions from the carrier board and
connector wiring not present in a final thin-film implant; thin-film interconnects
are also likely to have different (probably higher) resistance than the bench
wiring used here, so the actual power of a co-integrated implementation may differ
in either direction.

Signal recording was validated using a function generator input; validation with
real neural signals from electrodes lies outside the scope of firmware development.

\subsection{Future Directions}

PCB co-integration of the nRF52832 and Intan RHS2116 on a single substrate has
already been prototyped in the flex PCB described in Section~\ref{sec:results_noise}:
the two ICs are placed in close proximity with short inter-chip traces, directly
addressing the carrier board wiring that currently dominates WPT interference.
The immediate next step is therefore to correct the hardware fault in the current
revision (non-functional on-board oscillator) and characterise the flex PCB inside
the WPT field, which is expected to yield interference levels close to the
$\pm20$--$30$\,\textmu{}V already achieved in the direct on-chip measurement.
Beyond this, the design should be realised as a microfabricated device on a
thin-film substrate compatible with implantable electrode arrays, combining the
recording and stimulation electronics, the electrode interface, and the WPT
receiver components (RX coil, rectifier, and voltage regulation) in a single
compact, biocompatible assembly.

A separate firmware-level extension worth exploring is support for the full 32 channels
available on the headstage, which carries two Intan RHS2116 chips. The present firmware
uses only one. The headstage connector exposes two MOSI and two MISO lines (one pair
per chip) alongside a shared SCLK and CS. To drive both chips with the same
\texttt{CONVERT(63)} command, MOSI1 and MOSI2 would need to carry the same signal;
the simplest way to achieve this is a single solder bridge on the connector board tying
the two MOSI pins together, after which one SPI master drives both chips simultaneously.
The nRF52832 provides a SPI slave peripheral (SPIS) with EasyDMA on a separate
peripheral instance from the SPI master (SPIM), meaning both can operate concurrently.
A possible approach would then be to configure SPIS on instance~1 as a passive bus
listener alongside SPIM on instance~0: SPIS observes the same SCLK and CS, and
captures the second chip's MISO into its own EasyDMA buffer in parallel with the first.
After each DMA buffer swap, the two inactive buffers --- one per chip --- could be
copied interleaved to the ring buffer, producing a contiguous 32-channel data stream
(Ch01--Ch16 from chip~1, Ch17--Ch32 from chip~2) at the same SPI clock rate as the
current single-chip design. At 1\,kHz per channel, the total SPI transaction rate is
identical to the current 16-channel, 2\,kHz configuration, so no changes to the BLE
throughput budget or timing architecture would be required. A per-channel rate of
1\,kHz remains above the Nyquist frequency for LFP signals up to approximately
300\,Hz~\cite{reimann2013biophysically} and would therefore preserve the full signal
content of interest. This approach has not been implemented or tested and would require
the hardware modification described above; it is presented here as a plausible extension
path, not a validated result.
